Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-05-26 paper.tex
Updates from Overleaf

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/recombination_node_mrcas.pdf}
\caption{\label{fig:recomb_mrcas}
Date of common ancestry between the parents on either side of recombination
breakpoints, as a function of the divergence time between the parents.
MRCAs of parents associated with Pango designated recombinants (XA, etc)
are identified in orange. Larger symbols represent breakpoints in recombination
nodes which are ancestral to five or more samples.
Horizontal dotted lines show the four most common MRCA nodes,
which tend to be associated with major outbreaks and with many immediate children.
The stacked histogram shows the distribution of parental divergence times, ranging
from parents that have diverged only a handful of days previously, to much more
divergent parent lineages. See Figure~\ref{fig:recomb_mrcas_voc_breakdown}
for equivalent plots broken down by parental VoC classification.
}
\end{figure}

>>>>

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/recombination_node_mrcas.pdf}
\caption{\label{fig:recomb_mrcas}
Most recent common ancestor (MRCA) date for pairs of parents on either side
of a recombination breakpoint, as a function of the divergence time between parent
pairs. Breakpoints from recombination events caused by Pango designated recombinants
(XA, etc) are identified in orange. Larger symbols represent breakpoints from
recombination nodes which are ancestral to five or more samples.
Horizontal dotted lines show the four most common MRCA nodes; these
tend to be associated with major outbreaks and with many immediate children.
The stacked histogram shows the distribution of parental divergence times, ranging
from parents that have diverged only a handful of days previously, to much more
divergent parent lineages. See Figure~\ref{fig:recomb_mrcas_voc_breakdown}
for equivalent plots broken down by parental VoC classification.
}
\end{figure}
